Towards Performance-portable Parallel Programming in Computer Science Education

### 2020-01-22 src/2.Kokkos.tex
Commiting latest changes for review purposes.

\begin{figure}
\begin{Verbatim}[frame=leftline]
template <class ExecPolicy, class FunctorType>
Kokkos::parallel_for(
    const std::string& name, 
    const ExecPolicy& policy, 
    const FunctorType& functor);
\end{Verbatim}
\caption{The Kokkos parallel for loop class shows how template metaprogramming allows to specialize types. Its descriptive semantic offers the freedom to optimize execution on modern architectures with multiple degrees of concurrency where an Execution policy shapes the iteration space accordingly.}
\label{fig:parallelForKokkos}
\end{figure}

@@

>>>>

@@

\begin{figure}
\begin{Verbatim}[frame=leftline]
template <class ExecPolicy, class FunctorType>
Kokkos::parallel_for(const std::string& name, 
 const ExecPolicy& policy, 
 const FunctorType& functor);
template <class ExecPolicy, class FunctorType, class ReducerVarNonConst>
Kokkos::parallel_reduce(const std::string& name, 
 const ExecPolicy& policy, 
 const FunctorType& functor, 
 ReducerVarNonConst& reducer);
\end{Verbatim}
\caption{The Kokkos~\emph{parallel_for} and \emph{parallel_reduce} class show how template metaprogramming allows to specialize types. Its descriptive semantic offers the freedom to optimize execution on modern architectures with multiple degrees of concurrency where an Execution policy shapes the iteration space accordingly.}
\label{fig:parallelForAndReduceKokkos}
\end{figure}

WIP: Figure~\ref{fig:parallelForAndReduceKokkos} shows definitions of the~\emph{parallel for} and~\emph{parallel reduction} interfaces. Both interfaces take a set of template parameters and function arguments. \emph{ExecPolicy} shapes the iteration space for a particular device with varying degrees of hierarchical parallelism. A valid template parameter for ExecPolicy is a \emph{RangePolicy}. This type defines a 1-dimensional iteration range that is templated.  This allows to consider the distribtion of iterations into  hierarchical orghanization of parallel processing units. In this case, ExecPolicy is   and~\emph{FunctorType} and a set of function arguments.
